---
title: "git_7"
author: "Mia Fitzgerald"
date: "3/3/2026"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE) #change later with messages 
library(tidyverse)
library(knitr)
library(ggplot2)
```


### Filtering Color and Clarity 


```{r}
diamonds_clean <- diamonds %>%
  filter(color %in% c("D", "G", "J"), clarity %in% c("I1", "VS1", "IF"))

diamonds_clean %>%
  count(color, clarity) %>%
  kable()
  
```


^[Question 1 complete]


### Scatterplot of Price Versus Carat 


```{r}
diamonds_clean %>% 
  ggplot(aes(x = carat, y = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") 
  
```


Comment on the relationship between diamond price and weight (carat). 
^[Question 2 complete]


### Incorporating Diamond Color


```{r}
diamonds_clean %>% 
  ggplot(aes(x = carat, y = price, color = color)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") 
  
```


Comment on the relationship(s) between diamond price and weight for the different color qualities.
^[Question 3 complete]


### Incorporating Diamond Clarity


```{r}
diamonds_clean %>% 
  ggplot(aes(x = carat, y = price, color = color, shape = clarity)) +
  geom_point(alpha = 0.5) +
  geom_smooth(aes(linetype = clarity), method = "lm") 
  
```

Comment on the clarity and readability of the plot.
^[Question 4 complete]


### Incorporating Color and Clarity Through Grid Facet


```{r}
diamonds_clean %>% 
  ggplot(aes(x = carat, y = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") + 
  facet_grid(color ~ clarity)
  
```


Comment on the relationships between diamond price and weight for the different color qualities and clarities.
Which color-clarity combination has the steepest relationship?
^[Question 5 complete]


### Which Color-Clarity Combination has the Highest Price per Carat Ratio?


```{r}
diamonds_clean %>% 
  mutate(ppc = price / carat) %>%
  group_by(color, clarity) %>%
  summarize(avg_ppc = mean(ppc)) %>%
  arrange(desc(avg_ppc)) %>%
  kable()

```


Comment on whether the table generally agrees with your plots. 
^[Question 6 complete]


