---
title: "git_7"
author: "Mia Fitzgerald"
date: "3/3/2026"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE) 
library(tidyverse)
library(knitr)
library(ggplot2)
```


### Filtering Color and Clarity 


```{r}
diamonds_clean <- diamonds %>%
  filter(color %in% c("D", "G", "J"), clarity %in% c("I1", "VS1", "IF"))

diamonds_clean %>%
  count(color, clarity) %>%
  kable()
  
```


I used the diamonds dataset to filter for the specific colors and clarities for the new dataset. I used the new dataset to count the combinations of them. G and VS1 were far above everything else. 
^[Question 1 complete]


### Scatterplot of Price Versus Carat 


```{r}
diamonds_clean %>% 
  ggplot(aes(x = carat, y = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") 
  
```

The relationship between diamond price and weight is positive and linear. Meaning, as the weight of the diamond gets bigger, the more expensive it will be. 
^[Question 2 complete]


### Incorporating Diamond Color


```{r}
diamonds_clean %>% 
  ggplot(aes(x = carat, y = price, color = color)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") 
  
```


The diamond price of the color D tops the other colors in price. The colors G and J have a lower pricer per carat rate. 
^[Question 3 complete]


### Incorporating Diamond Clarity


```{r}
diamonds_clean %>% 
  ggplot(aes(x = carat, y = price, color = color, shape = clarity)) +
  geom_point(alpha = 0.5) +
  geom_smooth(aes(linetype = clarity), method = "lm") 
  
```


There is no clarity or readability of this plot due to the noise by all the different colors, shapes, and lines. I don't think this visual is something someone wants to look at for more than a second. 
^[Question 4 complete]


### Incorporating Color and Clarity Through Grid Facet


```{r}
diamonds_clean %>% 
  ggplot(aes(x = carat, y = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") + 
  facet_grid(color ~ clarity)
  
```


Adding the facet grid helped make out what specific combinations are lower or higher visually with regression lines. The color-clarity combination with the steepest relationship is D and IF. The graph also reflects how I1 is such a bad clarity. The J/G and I1 combination being the least steep. 
^[Question 5 complete]


### Which Color-Clarity Combination has the Highest Price per Carat Ratio?


```{r}
diamonds_clean %>% 
  mutate(ppc = price / carat) %>%
  group_by(color, clarity) %>%
  summarize(avg_ppc = mean(ppc)) %>%
  arrange(desc(avg_ppc)) %>%
  kable()

```


The table does agree with my plots. It is just harder to make out when it isn't expressed as a number. 
^[Question 6 complete] 


